### 2018-06-18 Thesis/Parts/Abstract/Abstract.tex
Results added
Thesis v0.1

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\section{Abstract}
[TODO: Abstract]
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Abstract}
Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain. Many studies have been done concerning the quality of word embeddings on general texts, such as wikipedia or review-websites. Giving promising results, the word embeddings have been studied and improved over resent years. However, these studies have been focused on generic text, overlooking the complexity of in-domain knowledge, such as rare domain specific words. This research focusses on the usefulness of word embeddings on domain specific texts, concerning scientific articles which have been published in 2017. This research compares the word embeddings  the TF-IDF algorithm on a corpus existing on a wide range of domain specific texts.
\end{document}

### 2018-06-18 Thesis/Parts/Conclusion/Conclusion.tex
Thesis v0.1

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Conclusion}
This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives for our categorization task, based on article titles. The TF-IDF alternatives give better results than the embeddings based on abstracts. The performance of the embeddings have been improved by weighting them with the TF-IDF values on word level. This improved embedding results in a median rank decrease of 8 on title and an median rank increase of 8 on title, compared to the best performing TF-IDF alternative.  The embedding also results in a memory decrease of 73.04\% making it more viable to keep it in memory.
We have furthermore shown that limiting vocabulary size to exclude rare words or common words decreases the performance of the embeddings. We thus come to the following conclusions:
\begin{enumerate}
\item{Article based embeddings perform better than TF-IDF on small texts}
\item{TF-IDF performs better than article based embeddings on larger texts}
\item{Embeddings give a significant decrease in memory usage compared to TF-IDF}
\end{enumerate}
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Conclusion}
This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives for our categorization task, based on article titles. The TF-IDF alternatives give better results than the embeddings based on abstracts. The performance of the embeddings have been improved by weighting them with the TF-IDF values on word level. This improved embedding results in a median rank decrease of 8 on title and an median rank increase of 8 on title, compared to the best performing TF-IDF alternative.  The embedding also results in a memory decrease of 73.04\% making it more viable to keep it in memory.
We have furthermore shown that limiting vocabulary size to exclude rare words or common words decreases the performance of the embeddings. We thus come to the following conclusions:
\begin{enumerate}
\item{Article based embeddings perform better than TF-IDF on titles, small texts, which contain limited information}
\item{TF-IDF performs better than article based embeddings on abstracts, larger texts, which contain more information}
\item{Embeddings give a significant decrease in memory usage compared to TF-IDF}
\end{enumerate}
\end{document}

### 2018-06-18 Thesis/Parts/Data/Data.tex
Thesis v0.1

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Data}
\subheader{Corpus}
The dataset we used for this research consists of all articles\footnote{From Elseviers corpus} published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications. This results in a total dataset of $1.391.543$ articles from $3.759$ journals.
\begin{table}[hbt]
\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
 & Total word count & Unique word count & Total token count & Unique token count \\
\hline
Title & $18.822.399$ & $939.665$ & $14.742.192$ & $230.805$ \\
\hline
Abstract & $264.653.020$ & $5.853.077$ & $171.474.473$ & $738.961$ \\
\hline
Total & $283.475.419$ & $6.209.769$ & $186.962.354$ & $763.475$ \\
\hline
\end{tabular}
\end{center}
\caption{Corpus size}\label{table:corpusSize}
\end{table}\\
The word occurrences follow the pattern of a pareto distribution as described by~\citet{wiegand2018word}. This distribution is visualized in XXXXXX, which displays the occurrences of the first 500 tokens of the corpus.
\includegraphics[width=6.5in]{Plots/word_occurrences}\\

\subheader{Datasets}
For this researched we used a (pre-made) tokenized dataset, which reduces the total amount of words by 34\%, from this tokenized set, we created the embeddings and the TF-IDF feature vectors.
\subsubheader{Tokenization}
The following steps have been applied to the words to create a tokenized set:
\begin{enumerate}
\item{Removed punctuation}
\item{Removed all non-ascii characters}
\item{Transformed all characters to lower-case}
\item{Removed stop-words, as provided by the NLTK library}
\item{Removed numbers}
\item{Stemmed all words, using the stemmer provided by the NLTK library}
\end{enumerate}
These transformations reduced our dataset by 34\%, resulting in a tokenized set of $186.962.354$ tokens.

\subsubheader{Embedding}
For this research we reused the word embeddings created by \citet{Truong2017Thesis}. These embeddings have a vector size of 300, which is an industry default. They have been trained on the entire Elsevier corpus, not limited to the subset we used for this research. To construct article embeddings we take the average of all normalized word embeddings for that article. Journal embeddings are constructed in the same way, we averaged all the normalized article embeddings to create the journal embeddings. We have used multiple embedding configurations for this research
\subsubsubheader{Default embedding}
The default embedding is created form the pre-trained word embeddings, no modifications have been applied to this set.
\subsubsubheader{TF-IDF embedding}
The TF-IDF weighted embedding set, referred to as TF-IDF embedding, are the default word embeddings weighted with a TF-IDF score per word.\\
The TF-IDF is calculated with a raw token count, and a smoothed inverted document frequency, calculated as follows:\\
\begin{equation}
IDF = \log_{10}(\dfrac{|A|}{|A_t|})
\end{equation}
Where $|A|$ is the total count of articles and $|A_t|$ is the count of articles containing term t.
The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value. Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word.
\subsubsubheader{10K TF-IDF embedding}
The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the amount of tokens it uses. This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, and with that increasing the performance.
\subsubsubheader{5K TF-IDF embedding}
The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to more aggressively limit the amount of tokens, and with that, cancel out more noise.
\subsubsubheader{1K-6K TF-IDF embedding}
The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words. The rationale for this is that common words will occur in many articles, creating noise, by cutting of the top 1.000 and cutting of everything below 6.000 we tried to reduce the noise by filtering common words. This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set.

\subsubheader{TF-IDF}
To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from pysparks the MlLib library. The TF-IDF feature vectors are created by hashing the tokens with the hasher, which has a set hash bucket size. These hashed values are passed on to the TF-IDF model, resulting in a feature vector which vector dimensions equals the amount of hash buckets. To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
We denote the TF-IDF configurations as follows: $vocabulary size/hashbucket size$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.\\
\includegraphics[width=6in]{Plots/tfidf_selection_plot}\\
The graph XXX shows the performance and storage size\footnote{in gigabyte, 1024 based} of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too. Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to.

\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Corpus}
The dataset we used for this research consists of all articles\footnote{From Elseviers corpus} published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications. This results in a total dataset of $1.391.543$ articles from $3.759$ journals.
\begin{table}[hbt]
\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
 & Total word count & Unique word count & Total token count & Unique token count \\
\hline
Title & $18.822.399$ & $939.665$ & $14.742.192$ & $230.805$ \\
\hline
Abstract & $264.653.020$ & $5.853.077$ & $171.474.473$ & $738.961$ \\
\hline
Total & $283.475.419$ & $6.209.769$ & $186.962.354$ & $763.475$ \\
\hline
\end{tabular}
\end{center}
\caption{Corpus size}\label{table:corpusSize}
\end{table}\\
The word occurrences follow the pattern of a pareto distribution as described by~\citet{wiegand2018word}. This distribution is visualized in XXXXXX, which displays the occurrences of the first 500 tokens of the corpus.
\includegraphics[width=6.5in]{Plots/word_occurrences}\\

\header{Datasets}
For this researched we used a (pre-made) tokenized dataset, which reduces the total amount of words by 34\%, from this tokenized set, we created the embeddings and the TF-IDF feature vectors.
\subheader{Tokenization}
The following steps have been applied to the words to create a tokenized set:
\begin{enumerate}
\item{Removed punctuation}
\item{Removed all non-ascii characters}
\item{Transformed all characters to lower-case}
\item{Removed stop-words, as provided by the NLTK library}
\item{Removed numbers}
\item{Stemmed all words, using the stemmer provided by the NLTK library}
\end{enumerate}
These transformations reduced our dataset by 34\%, resulting in a tokenized set of $186.962.354$ tokens.

\subheader{Embedding}
For this research we reused the word embeddings created by \citet{Truong2017Thesis}. These embeddings have a vector size of 300, which is an industry default. They have been trained on the entire Elsevier corpus, not limited to the subset we used for this research. To construct article embeddings we take the average of all normalized word embeddings for that article. Journal embeddings are constructed in the same way, we averaged all the normalized article embeddings to create the journal embeddings. We have used multiple embedding configurations for this research
\subsubheader{Default embedding}
The default embedding is created form the pre-trained word embeddings, no modifications have been applied to this set.
\subsubheader{TF-IDF embedding}
The TF-IDF weighted embedding set, referred to as TF-IDF embedding, are the default word embeddings weighted with a TF-IDF score per word.\\
The TF-IDF is calculated with a raw token count, and a smoothed inverted document frequency, calculated as follows:\\
\begin{equation}
IDF = \log_{10}(\dfrac{|A|}{|A_t|})
\end{equation}
Where $|A|$ is the total count of articles and $|A_t|$ is the count of articles containing term t.
The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value. Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word.
\subsubheader{10K TF-IDF embedding}
The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the amount of tokens it uses. This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, and with that increasing the performance.
\subsubheader{5K TF-IDF embedding}
The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to more aggressively limit the amount of tokens, and with that, cancel out more noise.
\subsubheader{1K-6K TF-IDF embedding}
The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words. The rationale for this is that common words will occur in many articles, creating noise, by cutting of the top 1.000 and cutting of everything below 6.000 we tried to reduce the noise by filtering common words. This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set.

\subheader{TF-IDF}
To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from pysparks the MlLib library. The TF-IDF feature vectors are created by hashing the tokens with the hasher, which has a set hash bucket size. These hashed values are passed on to the TF-IDF model, resulting in a feature vector which vector dimensions equals the amount of hash buckets. To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
We denote the TF-IDF configurations as follows: $vocabulary size/hashbucket size$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.\\
\includegraphics[width=6in]{Plots/tfidf_selection_plot}\\
The graph XXX shows the performance and storage size\footnote{in gigabyte, 1024 based} of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too. Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. The TF-IDF features are created on article level. We average the set of article embeddings to create a journal embedding.

\header{Pipeline}
We procesessed the TF-IDF sets an the embedding sets via the same pipeline, based on vector calculations. This ensures comparable results. The pipeline is setup as follows:
\begin{enumerate}
\item{Create training and validation set}
\item{Create journal embeddings}
\item{Categorize validation articles}
\item{Calculate performance metrics}
\end{enumerate}

\subheader{Create training and validation set}
We split our initial set  $80\%$ - $20\%$,. We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations. This split is based on a random number given to article each record, ensuring that all set have the same (random) training and validation set.
\subheader{Create journal embeddings}
From our training set we create the journal embeddings, which are created for most sets\footnote{see XXXXX} by averaging the article embeddings or feature vectors.
\subheader{Categorize validation articles}
To categorize the articles, we calculate the distance between the title- and abstract embedding of each article, from the validation set, to the title- and abstract embedding of each journal, during this process we keep track of:
\begin{itemize}
\item{Title-based-rank of the actual journal}
\item{Abstract-based-rank of the actual journal}
\item{Best scored journal on the abstract similarity}
\item{Best scored journal on the title similarity}
\item{Abstract similarity between the actual journal and the article}
\item{Title similarity between the actual journal and the article}
\end{itemize}
\subsubheader{Distance metrics}
To calculate the distance between to vectors, cosine similarity is commonly used CITATIONS NEEDED. We validated the quality of cosine similarity as a distance metrics by comparing it to all other similarity matrices available in the SciPy library, which we used to calculate the distances. We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set. XXXX shows the results of this validation.\\
\begin{minipage}{6.5in}
\begin{tabular}{|l|l|l|l|l|}
\hline
Metric\footnote{As defined and provided by the SciPy library} & Median title rank & Average title rank & Median abstract rank & Average abstract rank  \\
\hline
Braycurtis & 28 & 130 & 23 & 124  \\
\hline
Canberra & 33 & 148 & 26 & 133  \\
\hline
Chebyshev & 57 & 256 & 41 & 191  \\
\hline
\textit{Cityblock} & \textit{28} & \textit{130} & \textit{23} & \textit{124}  \\
\hline
\textit{Correlation} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
\textbf{Cosine} & \textbf{27} & \textbf{127} & \textbf{23} & \textbf{122}  \\
\hline
Dice & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Euclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Hamming & 1995 & 1929 & 1995 & 1929  \\
\hline
Jaccard & 1995 & 1929 & 1995 & 1929  \\
\hline
Kulsinski & 1995 & 1929 & 1995 & 1929  \\
\hline
Mahalanobis & 136 & 544 & 75 & 449  \\
\hline
Matching & 1995 & 1929 & 1995 & 1929  \\
\hline
Rogerstanimoto & 1995 & 1929 & 1995 & 1929  \\
\hline
Russellrao & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Seuclidean} & \textit{27} & \textit{124} & \textit{22} & \textit{115}  \\
\hline
Sokalmichener & 1995 & 1929 & 1995 & 1929  \\
\hline
Sokalsneath & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Sqeuclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Yule & 1995 & 1929 & 1995 & 1929  \\
\hline
\end{tabular}
\end{minipage}\\
These results show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& sqeuclidean). This similarity is expected, since the cosine and euclidean distances should yield the same results on normalized sets. The results show that some enhancement on the euclidean algorithm result in slightly improved results, although not significant XXX EXPLAIN? XXX. Also the Cityblock metric yields results close to the Cosine metric, it has a slightly worse performance, which is also not significant. Because of this, we will use the cosine-similarity as the distance matrix, which will make our results better comparable with other work.

\subheader{Performance measurement}
We use multiple metrics to validate the performance of the embedding sets and TF-IDF sets on the categorization task. These metrics are:
\begin{enumerate}
\item{F1-score}
\item{Median \& average rank}
\item{Rank distribution}
\end{enumerate}
\subsubheader{F1-score}
We define the positive \& negative metrics as follows:\\
\begin{jumpin}
$True Positive = $ Articles that are correctly matched to the current journal\\
$False Positive = $ Articles that are incorrectly matched to other journals\\
$False Negative = $ Articles that are incorrectly matched to the current journal\\
\end{jumpin}
We used these metrics to calculate the Recall, Precision \& F1 as follows:\\
\begin{jumpin}
$Recall = \dfrac{True Positive}{True Positive + False Negative}$\vspace{0.1in}\\
$Precision = \dfrac{True Positive}{True Positive + False Positive}$\vspace{0.1in}\\
$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall}$
\end{jumpin}
\subsubheader{Median \& average rank}
We use the median rank to indicate around which rank the 'standard' article would be ranked, based on its title or abstract. We do this by taking the median of the respective rank from each article. This gives us an indication of the behaviour of most articles in our validation set. This median rank (mostly) ignores the outliers, we therefore also use the average rank, which gives a more global indication, although this rank may be over-influenced by some outliers.
\subsubheader{Rank distribution}
To further analyse the ranking results, we plot the rank distribution to get an indication of the ranking-landscape.
\end{document}

### 2018-06-18 Thesis/Parts/Discussion/Discussion.tex
Thesis v0.1

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Discussion}
\subheader{1k 6k behaviour}
1k 6k embedding has lower storage than the other embeddings, this is most likely due to it's word filtering. Cutting off most-used words results probably in empty titles/abstracts which reduce the space that is needed for this embedding variant. All other embeddings have the same size, which indicates that this does not occur in the other situations, even in the 5k set, where the same amount of words are cut off.\\
The, relatively, much higher average rank compared to the median rank of the 1k 6k embedding can be explained with the data of table (RANKING DISTRIBUTION TABLE). This shows that the embedding goes up at the start, indicating that there are articles in the low ranks, flats out in the center more than the others do, indicating a relatively low amount of articles in the middle ranks, and a strong increase at the end. Indicating that there are  many titles on the high end of the distribution. This explains the relatively low median, which is dawn towards the lower end of the distribution, and the high average, which is drawn to the higher end of the distribution.

\subheader{Best performers}
The data shows that the 10.000/10.000 set preforms better than all other TF-IDF sets, although the difference with the 5.000/10.000 is low, 1 (7.14\%) on abstract and 3 (8.57\%) on title. For the embeddings the TF-IDF weighted embedding works better than the others, although it is near equal to the default embeddings, which 1 rank higher on abstract, and equal on title.

\subheader{TF-IDF weighting on embeddings}
The difference between the TFIDF weighted embedding and the default embedding can be explained as follows:
The embeddings seem to outperform the TF-IDF in situation when there is little information available, the titles in our case. This indicates that the embeddings store some kind of word meaning that enables them to perform relatively well on the titles. The abstracts on the other hand contain much more information. Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information. If this is the case, we could expect that there would little performance increase on the title, since the TF-IDF lacks the information to perform well. This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a major one. We could expect on the abstract an increase in performance, since the TF-IDF has more information in this context. We would expect that the weighting applied by the TF-IDF improves the performance of the embedding by indicating word importance. Our data shows a minor improvement in performance of 1(4.35\%) median rank and 10(6.41\%) average ranks.

\subheader{Raw, readable results}
The TF-IDF outperform the embeddings on the abstract with a difference of 8 ranks for the best of each. On the title however, the best embedding outperforms the best TF-IDF by 8 ranks.

\subheader{Memory usage}
Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings. The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10.000/10.000 uses 11.61 GB, which is 270.93\% more. The closest TF-IDF configuration we used was 1.000/1.000, which uses 5.13 GB (SEE GRAPH XXX). This TF-IDF set has a median title rank of 183 and a median abstract rank of 44. Which is worse than the embedding, which also uses less memory.

\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Discussion}
\subheader{Sets}
\subheader{Best performers}
The data shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank (7.14\%) on abstract and 3 median ranks (8.57\%) on title. For the embeddings the TF-IDF weighted embedding works better than the others, although it is has is not a significant improvement compared to the default embeddings, which 1 median rank higher on abstract, and equal on title.
\subsubheader{TF-IDF}
The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings ourperform the TF-IDF feature vectors on the title. The main difference between the abstract \& title is that the title contains less unique tokens (see XXXXX), this means that the titles contain less unique information, making them more generic. Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts cannot differentiate between the highly similar titles. The TF-IDF method works better on the abstract, which contain more unique words, which help in differentiating the different texts. Furthermore, increasing the vocabulary size increases the performance of the TF-IDF, since the vocabulary size is cut-off at word occurrences, which reduces the amount of unique words. 
\subsubheader{Embedding}
\subsubsubheader{Limited tfidf embeddings}
The limited TF-IDF embeddings all under perform, compared to the non-limited TF-IDF embedding, on the median and average ranking. Indicating that the noise reduction is too much, and it removes meaningful words. If the noise reduction would be too low, we would only see a slight increase or none at all. However, the rank lowers, indicating the reduction in embedding quality due to missing words. However, graphs XXX and XXX show that their rank distribution is different from the other embeddings. Their pattern show a decent performance indicates the following pattern: a high/average performance on the top-rankings, an under performance on the middle rankings and  a resulting stack-up of articles with a high-ranking. This is further supported by the TF-IDF score on titles (Graph XXX), on which the limited TF-IDF embeddings are the top performance. Indicating a better performance on the top-1 articles compared to the other sets.\\This leads us to believe that the cut-off was effective, but that is did not suit our purpose. The cut-off moved the "middle-ranked"  articles to either the high end of the rankings, or the lower end. Resulting in low median and average scores, but in (relatively) high accuracy scores. The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding. This indicates that only the 1K-6K cut actually removes entire titles and/or abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros. However they can be processed more efficiently during calculations}. This results in a lower memory requirement.

\subsubheader{TF-IDF \& embeddings}
The difference between the TFIDF weighted embedding and the default embedding can be explained as follows:
The embeddings seem to outperform the TF-IDF in situation when there is little information available, the titles in our case. This indicates that the embeddings store some kind of word meaning that enables them to perform relatively well on the titles. The abstracts on the other hand contain much more information. Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information. If this is the case, we could expect that there would little performance increase on the title, since the TF-IDF lacks the information to perform well. This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a major one. We could expect on the abstract an increase in performance, since the TF-IDF has more information in this context. We would expect that the weighting applied by the TF-IDF improves the performance of the embedding by indicating word importance. Our data shows a minor improvement in performance of 1(4.35\%) median rank and 10(6.41\%) average ranks.

\subheader{Memory usage}
Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings. The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding. The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (SEE GRAPH XXX). This TF-IDF set has a median title rank of 183 and a median abstract rank of 44. Which is worse than the embedding, which also uses less memory.
\end{document}

### 2018-06-18 Thesis/Parts/Research_results/Research_results.tex
Results added
Background, motivation and related work
Thesis v0.1

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Research results}
\subheader{Ranking}
\includegraphics[width=6in]{Plots/Abstract_rankings}\\
\\
\includegraphics[width=6in]{Plots/Title_rankings}\\
\subheader{Rank distribution}
\includegraphics[width=6in]{Plots/Abstract_rank_distribution}\\
\\
\includegraphics[width=6in]{Plots/Title_rank_distribution}\\
\subheader{F1-Score}
d
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Research results}
\subheader{Ranking}
The graph XXX shows the ranking results for the different sets based on the title. Graph XXX displays the ranking results based on the abstract. Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.\\
\includegraphics[width=6.5in]{Plots/Title_rankings}\\
\vspace{0.2in}\\
\includegraphics[width=6.5in]{Plots/Abstract_rankings}\\
\clearpage
\subheader{Rank distribution}
Graph XXX shows the rank distribution for the titles on, graph XXX shows this for the ranks based on the abstract. Both graphs use a logarithmic scale. These graphs give a detailled view of the ranks presented in the respective graphs XXX and XXX.\\
\includegraphics[width=6.5in]{Plots/Title_rank_distribution}\\
\vspace{0.2in}\\
\includegraphics[width=6.5in]{Plots/Abstract_rank_distribution}\\
\clearpage
\subheader{F1-Score}
The graphs XXX and XXX show the F1 score for the title and abstract respectively. These scores are the average journals scores for each set, indicating the quality of the sets for absolute hits (top-1).\\
\includegraphics[width=6.5in]{Plots/Title_avg_f1}\\
\vspace{0.2in}\\
\includegraphics[width=6.5in]{Plots/Abstract_avg_f1}\\
\clearpage
\subheader{Memory usage}
XXX shows the total memory usage of each \textit{Validation set}, indicating their costs in memory storage \& RAM.\\
\begin{tabular}{|l|l|}
\hline
Set & Size in GB\\
\hline
tfidf 5k 5K & $9.82$ \\
\hline
tfidf 5K 10K & $11.47$ \\
\hline
\textbf{tfidf 10K 10K} &\textbf{11.61}\\
\hline
embedding & $3.13$ \\
\hline
5k embedding & $3.13$ \\
\hline
10k embedding & $3.13$ \\
\hline
\textbf{tfidf embedding} & \textbf{3.13} \\
\hline
1k 6k embedding & $3.06$ \\
\hline
\end{tabular}
\\

\end{document}

### 2018-06-18 Thesis/Parts/Research_setup/Research_setup.tex
Thesis v0.1

\header{Experiment setup}
We used the following pipeline to collect the performance metrics for the categorization task:
\begin{enumerate}
\item{Create embeddings}
\item{Filter articles}
\item{Create training and validation set}
\item{Create journal embeddings}
\item{Categorize validation articles}
\item{Calculate performance metrics}
\end{enumerate}

\subheader{Filter articles}
We create our initial set of articles by collecting all articles from the journals that were published in the year 2017, and have at least 200 publications in 2017. This reduces the journal set to $3,759$ thousand journals, resulting in a set of $1,391,543$ million articles ().
\subheader{Create training and validation set}
We split our initial set  $80\%$ - $20\%$,. We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations.
\subheader{Create journal embeddings}
From our training set we create the journal embeddings by averaging all title embeddings as the journal title embedding, and by averaging all abstract embeddings as the journal abstract embedding. We also normalized both embeddings. 
\subheader{Categorize validation articles}
To categorize the articles, we calculate the distance between the title- and abstract embedding of each article, from the validation set, to the title- and abstract embedding of each journal. To calculate the distance, we use cosine similarity (as provided by the SciPy library\cite{SciPy}). During this process we keep track of:
\begin{itemize}
\item{Title-based-rank of the actual journal}
\item{Abstract-based-rank of the actual journal}
\item{Best scored journal on the abstract similarity}
\item{Best scored journal on the title similarity}
\item{Abstract similarity between the actual journal and the article}
\item{Title similarity between the actual journal and the article}
\end{itemize}
\subheader{Performance measurement}
We use multiple metrics to indicate the performance of the embeddings on a categorization task. These metrics are:
\begin{enumerate}
\item{F1-score}
\item{Median \& average rank}
\item{Rank distribution}
\end{enumerate}
\subsubheader{F1-score}
We define the positive \& negative metrics as follows:\\
\begin{jumpin}
$True Positive = $ Articles that are correctly matched to the current journal\\
$False Positive = $ Articles that are incorrectly matched to other journals\\
$False Negative = $ Articles that are incorrectly matched to the current journal\\
\end{jumpin}
We used these metrics to calculate the Recall, Precision \& F1 as follows:\\
\begin{jumpin}
$Recall = \dfrac{True Positive}{True Positive + False Negative}$\vspace{0.1in}\\
$Precision = \dfrac{True Positive}{True Positive + False Positive}$\vspace{0.1in}\\
$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall}$
\end{jumpin}
\subsubheader{Median \& average rank}
We use the median rank to indicate around which rank the 'standard' article would be ranked, based on its title or abstract. We do this by taking the median of the respective rank from each article. This gives us an indication of the behaviour of most articles in our validation set. This median rank (mostly) ignores the outliers, we therefore also use the average rank, which gives a more global indication, although this rank may be over-influenced by some outliers.
\subsubheader{Rank distribution}
To further analyse the ranking results, we plot the rank distribution to get an indication of the ranking-landscape. We limit ourselves to the following categories: 1 (absolute hits), top-10, top-20, top-30, top-40, top-50,  top-100 and 100+. 
\end{document}

>>>>

\header{Experiment setup}

\end{document}
